### 2022-06-13 paper.tex
add discussion

%Here we propose a number of new methods for the analysis of single cell methylation data and provide them to the research community as a command line tool called \texttt{scbs}.
%Instead of dividing the genome into coarse-grained tiles, we propose to discover variably-methylated regions (VMRs) in the data itself, which improves performance of common downstream applications.
%We also think that VMRs, due to their smaller size, are easier to interpret than  and furthermore provides a list of candidate regions.
%These regions may then be linked to individual genes, tested for celltype-specific methylation differences, or subjected to gene ontology or motif enrichment, depending on the research question at hand.
%We also propose a number of methods specifically tailored to the sparse nature of scBS data.
%First, we observe

%- propose a number of new methods for the analysis of scBS data
%- developed methods to analyse scBS data that go beyond simple genome tiling
% - instead we discover potential genomic regions of interest on the data itself, which improves performance of common downstream applications and aids interpretability.
% - VMRs can also be used as input for e.g. motif enrichment, go enrichment etc
%- devised a method to store genome-wide scBS data efficiently
%- propose a new measure of DNA methylation in a genomic interval (~ relative methylation)

%- implement them in Python and release them to the community as a Python package with a CLI
%-> no more custom scripts and manual data wrangling of 1000 text files required, instead every user can quickly go from raw data to count matrix
%- lowers the entry barrier for scBS data analysis and makes this new and exciting data type available to a greater audience

%whats missing?
%-

>>>>

Here we propose a number of new methods for the analysis of single cell methylation data and provide them to the research community as a command line tool.
Instead of dividing the genome into coarse-grained tiles, we propose to discover variably-methylated regions (VMRs) in the data itself, which improves performance of common downstream applications.
VMRs help interpreting the results of scBS experiments, since they represent a list of candidate regions that are potentially biologically meaningful.
Due to their smaller size, individual VMRs can also be related to nearby or intersecting genomic features such as gene bodies or known regulatory elements.
Furthermore, VMRs can be tested for methylation differences between groups of cells, or subjected to gene ontology enrichment or motif enrichment, depending on the research questions at hand.

We also propose a number of methods to address issues caused by the sparse nature of scBS data.
First, we observe that incomplete read coverage of a genomic interval can lead to inaccurate methylation estimates.
To remedy this problem, we propose to use relative methylation values instead of absolute methylation fractions, and to employ shrinkage to decrease the impact of intervals with very low sequencing coverage.
Second, we suggest a method to handle missing values in PCA in an iterative manner.
Both of these methods help remedy the influence of differences in sequencing coverage on dimensionality reduction and clustering.

Finally, we provide the above-mentioned methods to the scientific community in the form of a command line tool.
Our software, called \texttt{scbs}, allows the user to obtain a cell \times region matrix from raw methylation files using only few, simple shell commands
This means that users no longer need to write custom data-wrangling scripts, which ensures reproducibility across and makes the analysis of single-cell methylomes faster and easier.
